pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-28 article.tex
Improved pipeline figure, fix https://github.com/richelbilderbeek/pirouette_article/issues/9

\begin{sidewaysfigure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
  pirouette pipeline
  \giovanni{
  see \texttt{https://github.com/richelbilderbeek/pirouette\_article/issues/9}
  }
  }
  \label{fig:pipeline}
\end{sidewaysfigure}

@@

The third step infers a Bayesian posterior from the simulated alignment,
using the inference model(s) selected in the previous step. The user
can specify the additional parameters needed for the BEAST2 run, which
are the Markov-Chain Monte Carlo (MCMC) setup, 
an optional Most Recent Common Ancestor (MRCA) \giovanni{MRCA has been already been defined. It is therefore possible to use the acronym only, if you want} prior and an RNG seed.
The MCMC setup determines the number of posterior trees sampled.
An MRCA prior allows the inferred phylogeny to have a dated crown age.

@@

A first research question that \verb;pirouette; answers is:
"What is the error BEAST2 makes \giovanni{I would prefer "the error made by BEAST2" in place of "the error BEAST2 makes"} from a phylogeny using the same diversification model as it was generated by?"

\iffalse
We start with an idealised \giovanni{the word idealized cannot be used unless we specify what it means.} Yule (pure-birth) tree 
with five taxa and a crown age of ten.
By idealized, we mean a phylogeny that is easiest to recover
by the Bayesian inference. A phylogeny that is easy to recover has
the most common branch length distribution imaginable. We
use an idealised tree, as we want to measure the baseline noise; that is, the lowest error that BEAST2 can possibly make.
\fi

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    pirouette pipeline
  }
  \label{fig:pipeline}
\end{figure}

@@

The third step infers a Bayesian posterior from the simulated alignment,
using the inference model(s) selected in the previous step. The user
can specify the additional parameters needed for the BEAST2 run, which
are the Markov-Chain Monte Carlo (MCMC) setup, 
an optional MRCA prior and an RNG seed.
The MCMC setup determines the number of posterior trees sampled.
An MRCA prior allows the inferred phylogeny to have a dated crown age.

@@

A first research question that \verb;pirouette; answers is:
"What is the error made by BEAST2 from a phylogeny using the same diversification model as it was generated by?"
